%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  \vspace{5mm}
  \cventry
    {Associate Director Technology}
    {MSys Technologies}
    {Pune ,MH , India}
    {Oct 2023 - Currently Employed}  
    {
      \begin{cvitems}
        \item Working as the customer point of contact for engagements.
        \item Lead the pre-sales team create client proposals , execute POC and technology evaluations , create capability decks for various customers.
        \item Resolving technical and nontechnical customer escalations.
        \item Lead the discovery phase and post discovery planning and documentation. Also take part in architectural definition and requirement gathering of green field projects.
        \item Taking care of recruiting the right talent for the customer engagements and sales activities.
        \item Mentoring developers and ensuring software quality is maintained in the deliverables and on expected timelines.
        \item Taking active part in customer proposals , costing , project estimations and feasibility.
        \item \textbf{Resolved a severe escalation for Autodesk client where in customer wanted automation implemented for their Network monitoring team , got the required automation developed with customer satisfaction.}
      \end{cvitems}
    }
  
  \vspace{4mm}
  \cventry
    {Senior Architect Technology}
    {BlueConch Technologies - Xpansion - UST }
    {Pune ,MH , India}
    {June 2021 - Oct 2023}
    {
        \begin{cvitems}
          \item Working as Architect for Dematic simulation team . Lead the efforts to modernize their  simulation solution .
          \item Executed the technology assessment for EXO Checkout RFID product . Suggested improvements to mitigate the performance issues and help in attaining the long term vision for the product. Helping India development team in setting up local environments and solving their technical queries. Future release and feature planning.
          \item \textbf{Resolved multiple technical issues for the EXO client which I had identified during technical Assessment.}
          \item Lead the “Software Discovery team” for the Deluxe “Remote Deposit Capture” product.
          \item Analyzed the current system architecture and created detailed technical analysis documentation. Proposed a new solution for the technology revamp in order to remove the obsolete          
          \item ActiveX components and move the solution to use modern WebUI using ReactJS . Worked on the time / resource utilization estimations.
          \item \textbf{Instrumental in adding 30+ team members in the Deluxe account.}
          \item Lead the transition of Rand McNally ”Connected Vehicle” product to BlueConch from 3rd party vendor.
          \item Understood the architecture of the product and acquired detailed technical understanding of the various sub components . Trained the BlueConch team to take over the product development and services of the product.
          \item Proposed new high-performance architecture to resolve performance issues. The proposed stack consists of NodeJS ,TimeSeries databases , MQ and bespoke reporting services to be developed using a cloud agnostic approach.
        \end{cvitems}
    }
  \vspace{4mm}

  \cventry
    {Principle Software Engineer}
    {SevOne - Jeavio India Pvt Ltd}
    {Pune ,MH , India}
    {Sep 2020  - June 2021}  
    {
      \begin{cvitems}
        \item Working as part of the \textbf{SevOne} escalations team for the NMS product , resolving client escalations , performing root cause analysis and software performance issues.
        \item Platform related fixes and working on vulnerability resolution.
      \end{cvitems}
    }  

  \cventry
    {Technical Architect / Technology Specialist}
    {Cognizant Technology Solutions}
    {Pune  , India , USA}
    {Sept 2011 - Sept 2020}
    {
      \begin{cvitems}
        \item \textbf{Aug 2018 - Nov 2019 : Pune}          
        \item Architect for developing and implementing the \textbf{Cognizant SmartAPM} solution for Kohls US.
        \item Designed and developed a python based metric collector to collect KPI data from Kohls Splunk and push the KPI data to Influx DB in SmartAPM consumable form. Parallelized the metric collector to query multiple metrics at the same time and reduced the time to query.      
        \item Integrated the SmartAPM notification engine with \textbf{ServiceNow}.        
        \item \textbf{Nov 2017 - 15 July 2018: Chandler AZ}                
        \item Worked as part of the SVT classic team in Wells Fargo.
        \item Work involves bug fixing and feature development for the Wells Fargo front office user interface using QT framework.
        \item Fixing bugs in Perl , Python report generators and log analyzers              
        \item \textbf{May 2016 - Feb 2017: Atlanta}                
        \item Worked on Internet of Things and Edge Computing architecture and proof of concept development.
        \item \textbf{March 31 2015 - May 2016 : Atlanta}                
        \item Worked in CNN - Turner broadcasting systems as onsite tech lead for the "Editorial Events" team . Worked on bug fixes and feature development for Turner - CNN.com website.
        \item Coordinating with on-site and offshore teams . Resolving teams technical issues. Proposing and getting solutions based on MEAN stack such as REST web services development , maintenance using NodeJS ,  Legacy data migration scripting using Perl/Python.                
        \item \textbf{Sep 2011 - March 31 2015 : Pune}                
        \item Worked on various POC developments utilizing the Eucalyptus Cloud and VMWare VCenter.
        \item Developed WalBox cloud storage application that allows users to store files on Eucalyptus Walrus block storage or Amazon S3 using Python.Developed the Windows user interface using Python/Tk library for the same product
        \item Working on  developing the RESTful web services for Cognizant Social Tango using Node.JS and RethinkDB.Developed engine to store and generate the Activity Streams 2.0 compliant streams using nodejs and RethinkDB. Engine pre-created the activity stream instead of generating them on user demand.                
      \end{cvitems}
    }

  \cventry
    {Staff Product Developer}
    {BMC Software}
    {Pune , India}
    {Oct 2009 - Aug 2011}        
    {
        \begin{cvitems}
          \item Worked  in the BMC Performance Assurance product line mainly working on the data metric collection module.
          \item Developed support for the Citrix Xen platform metric collector and multiple other metrics.
          \item Worked  on bug fixes , new feature feasibility analysis and development , with primary focus on Linux and Solaris platform
        \end{cvitems}
    }

  \cventry
    {Associate Projects}
    {Cognizant Technology Solutions}
    {Pune , India}
    {Jan 2008 - Oct 2009}    
    {
        \begin{cvitems}
          \item Developed applications and tools for the Credit Suisse US Equities booking team which includes EOD B2B trade processors ,real-time data migration tool , report generators and worked on various bug fixes.
        \end{cvitems}
    }

  \cventry
    {Senior Software Engineer}
    {Symphony Services}
    {Pune , India}
    {May 2006 - Jan. 2008}    
    {
      \begin{cvitems}
        \item Worked as part of the platform team for the development of the Kazeon search appliance
        \item Back porting Kazeon specific kernel changes. Ported the CCISS driver from 2.6 to 2.4 kernel.Fixed Broadcom Network card driver issues. 
        \item Developed a  system configuration interactive Perl script to configure the Kazeon Appliance. The script configures the Hostname, IP Addresses, DNS, routes and static routes etc.Worked on Bug Fixes for various components in the Kazeon software.
      \end{cvitems}
    }

  \cventry
    {Member of Technical Staff}
    {Persistent Systems Pvt. Ltd.}
    {Pune , India}
    {March . 2005 - May. 2006}      
    {
      \begin{cvitems}
        \item Applied Identity Project : Porting Windows application to Mac OS X. Project involved porting the GUI from Windows to Mac , porting the service to Mac.
        \item Mirapoint Project : Changed cpio and tar source code to add support for long file path handling capabilities. Made changes in cpio code to remove this limitation.Worked on Bug fixes for some components in Mirapoint code.Reiser4 file system evaluation. Created system feasibility report for this file system to be used for client appliance. Calculated statistical result in text as well as graphical formats to represent the file system statistics. Comparing the results with ext3 and UFS as control values.
      \end{cvitems}
    }

  \cventry
    {Member of Technical Staff}
    {Calsoft Private Limited}
    {Pune , India}
    {Dec 2003 - Dec 2004}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Developed TCL based dynamic loadable modules in C for interacting with PANASAS NAS server. Work involved programming in C and TCL. The target NAS Server operating system is based on the FreeBSD. Wrote a Framework for Firing the NFS RPC using the TCL interpreter and the Application framework.
        \item Developed a remote network configuration using the \hyphenation{ C Expect } Interface for configuring the NAS server.
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
