\documentclass[a4,11pt]{cv4tw}
\usetheme[gray]{sharp}
\setmystyle[assetbullet]{\color{icons}\faBook}
\setmystyle[fieldratefull]{\color{icons}\faCircle}
\setmystyle[fieldrateempty]{\color{icons}\faCircleBlank}
\setmystyle[custom0bullet]{\color{icons}\faBolt}
\setcvcontact[email]{abhijeet.sane@cognizant.com} 
\setcvcontact[cellphone]{+1 404 563 4053}
\setcvcontact[address]{Chandler , AZ} 
\usepackage{inputenc}
\firstname{Abhijeet}
\lastname{Sane}
\quote{\itshape Software developer with 14+ years of experience in designing and implementing highly scalable distributed systems. Have internal knowledge of Unix/Linux and good working knowledge of MEAN stack based applications. Have good communication skills and capacity to work as team lead or individual contributor roles.}

\setcvasset[0]{\emph{Software Developer}}
\pdfminorversion=5
\pdfcompresslevel=9 
\pdfobjcompresslevel=3
\begin{document}

\section{Skills}

\begin{skills}{}
      \skill[Scripting Languages ] {Shell Scripting, Perl , Python , NodeJS,\LaTeX}
      \skill[Programming Languages ]{C , C++ }
      \skill[Operating Systems] { Linux Kernel 2.4.X / 2.6.X, FreeBSD, DOS, Windows 9X / XP}
      \skill[Virtualization] { VMware AppDirector }
      \skill[Frameworks]{ Hapi }
      \skill[Cloud Technologies] {Citrix Xen , Amazon EC2 , Eucalyptus}
      \skill[Database] {MySQL ,PostgreSQL, RethinkDB , Cassandra}
      \skill[Caching] {Redis}
      \skill[Gui ] {QT Toolkit , Python/Tk} 
      \skill[Tools]{GIT , CVS }
      \skill[Others]{Open Source , High performance architectures , Estimation , System integration , HTTP- REST } 
\end{skills}


\section{Work Experience}
\story{Principal Software Engineer}{Cognizant Technology Solutions}{Feb 2017 - Current \\ Chandler , AZ}
{Languages / Technologies \\Perl , Python , C/C++ , QT , Linux ,Javascript}
	{ 
	\begin{missions}
		\item Worked as part of the SVT classic team in Wells Fargo.
		\item Work involves bug fixing and feature development for the Wells Fargo front office user interface using QT framework.
		\item Fixing bugs in Perl , Python report generators and log analyzers
	\end{missions}
}


\story{Technical Architect}{Cognizant Technology Solutions}{May 2016 - Feb 2017 \\ Atlanta , GA}
{Languages / Technologies \\ IoT , Linux , NodeJS, Edge Computing , Analytics }
	{ 
	\begin{missions}
		\item Worked on Internet of Things and Edge Computing architecture and proof of concept development.
		\item Worked as part of the architect team for Associated Press (one of the worlds largest news gathering organizations). 
	\end{missions}
}

\story{Onsite Lead (CNN-Turner)- Coordinator}{Cognizant Global Technnology Office}{March 31 2015 - May 2016 \\ Atlanta , GA}
{Languages / Technologies \\ NodeJS/Perl/Python/Redis/Linux}
	{ 
	\begin{missions}
		\item Worked in CNN - Turner broadcasting systems as onsite tech lead for the "Editorial Events" team . Worked on bug fixes and feature development for Turner - CNN.com website.
		\item REST web services development and maintenance using NodeJS
		\item Legacy data migration scripting using Perl and python.
		\item Coordinating with on-site and offshore teams . Resolving technical issues.
		\item Proposing and getting solutions based on MEAN stack implemented.
	\end{missions}
}

\story{Technology Specialist}{Cognizant Technology Solutions}{Sep 2011 - March 31 2015 \\ Pune , India}
{Languages / Technologies \\ NodeJS/Python/Perl/Redis/}
	{ 
	\begin{missions}
		\item Worked as part of the GTO JPaaS team for development of the CloudSet product.Worked on the Eucalyptus Cloud and VMWare VCenter related assignments.
		\item Developed WalBox cloud storage application that allows users to store files on Eucalyptus Walrus block storage or Amazon S3 using Python.Developed the Windows user interface using Python/Tk library for the same product
		\item Developed the VMware AppDirector templates for the Cognizant Build as A Service ( BaaS) product.
		\item Worked on the Glitz POC for age and gender classification.Developed the reference implementation for gender and age classification using OpenCV and C/C++
		\item Developed the database schema for the AR content repository application in MySQL and the RESTful web services in Python . Also worked on the Android application POC development using the Google analytics library.
		\item Working on  developing the RESTful web services for Cognizant Social Tango using Node.JS and RethinkDB.Developed engine to store and generate the Activity Streams 2.0 compliant streams using nodejs and RethinkDB. Engine pre-created the activity stream instead of generating them on user demand.
	\end{missions}
}

\story{Staff Product Developer}{BMC Software}{Oct 2009 - Aug 2011\\ Pune , India}
{Languages/Technologies \\ C/C++/Python/Perl}
	{ 
	\begin{missions}	
		\item Worked  in the BMC Performance Assurance product line mainly working on the data metric collection module.
		\item Developed support for the Citrix Xen platform metric collector and multiple other metrics.
		\item Worked  on bug fixes , new feature feasibility analysis and development , with primary focus on Linux and Solaris platform
		\item Work also involved improving the code to use newer features available in language and compiler set.
	\end{missions}
}

\story{Associate Projects}{Cognizant Technology Solutions}{Jan 2008 - Oct 2009\\ Pune , India}
{Languages / Technologies \\ C/C++/Perl}
	{ 
	\begin{missions}
		\item Developed applications and tools for the Credis Suisse US Equities booking team.
		\item EOD B2B trade processors and real-time data migration tool.
		\item Developed Report generators , Worked on various bug fixes and code reviews.
		\item US Booking subsystem stability checker tools.
	\end{missions}
}

\story{Senior Software Engineer}{Symphony Services }{May 2006 - Jan. 2008\\ Pune , India}
{Languages/Technologies \\ C/Perl/Shell/Linux}
	{ 
	\begin{missions}		
		\item Worked as part of the platform team for the development of the Kazeon search appliance
		\item Ported the changes made by Kazeon in Linux 2.4.18 kernel to 2.6. The changes included porting some Kazeon Appliance specific Sys-Calls and changes in the CIFS and NFS modules.
		\item Ported the CCISS driver from 2.6 to 2.4 kernel.
		\item Worked on Broadcom Network card driver issues. Some of the required ETHTOOL ioctl's were not supported in the driver code. Made changes in the card driver code to support ethtool use.
		\item Ported the Dell Open Manage related Linux drivers to Red-Hat Linux 9.0.
		\item Developed a  system configuration interactive Perl script to configure the Kazeon Appliance. The script configures the Hostname, IP Addresses, DNS, routes and static routes etc.
		\item Worked on Hardware qualification of Fujitsu and HP DL 360 machines for the Kazeon software.
		\item Worked on Bug Fixes for various components in the Kazeon software.	
	\end{missions}
}

\story{Member of Technical Staff}{Persistent Systems Pvt. Ltd.}{March . 2005 - May. 2006\\ Pune , India}
{Languages/Technologies \\ C/Perl/Shell/Linux}
	{ 
	\begin{missions}		
		\item Worked as part of the platform team for the development of the Kazeon search appliance
		\item Applied Identity Project : Porting Windows application to Mac OS X. Project involved porting the GUI from Windows to Mac , porting the service to Mac.
		\item Mirapoint Project : Changed cpio and tar source code to add support for long file path handling capabilities. Made changes in cpio code to remove this limitation.
		\item Mirapoint Project : Worked on Bug fixes for some components in Mirapoint code.
		\item Mirapoint Project : Reiser4 file system evaluation. Created system feasibility report for this file system to be used for client appliance. Calculated statistical result in text as well as graphical formats to represent the file system statistics. Comparing the results with ext3 and UFS as control values.
	\end{missions}
}

\story{Member of Technical Staff}{Calsoft Private Limited}{Dec 2003 - Dec 2004.\\ Pune , India}
{Languages/Technologies \\ C/TCL/FreeBSD}
	{ 
	\begin{missions}		
		\item Developed TCL based dynamic loadable modules in C for interacting with PANASAS NAS server. Work involved programming in C and TCL. The target NAS Server operating system is based on the FreeBSD. Wrote a Framework for Firing the NFS RPC using the TCL interpreter and the Application framework.
		\item Developed a remote network configuration using the \hyphenation{ C Expect } Interface for configuring the NAS server.
		\item Developing / fixing C programs which were part of the test framework.
	\end{missions}	
}	


\section{Education}

\story{Master in Computer Applications }{IGNOU \\ Grades: 63.67\%}{2002 - 2004\\Pune,India}{}{}
\story{Bachelor in Science ( Chemistry) }{University Of Pune \\ Grades: 58\%}{1996 - 1999\\Pune,India}{}{}
\story{H.S.C}{Maharashtra Board \\ Grades: 75\%}{1996 \\Pune,India}{}{}
\story{S.S.C}{Maharashtra Board \\ Grades: 80\%}{1994 \\Pune,India}{}{}


\end{document}

